% !TEX program = xelatex

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\name{Joey Lorich}
\address{joey@lorich.me}
\address{linkedin.com/in/jlorich}
\address{github.com/jlorich}

\begin{document}
\vspace{-1em}
%----------------------------------------------------------------------------------------
%	Profile
%----------------------------------------------------------------------------------------
\begin{rSection}{Profile}
  
  Visionary technology executive with a distinguished record of driving innovation, growth, and transformation in dynamic, high-tech environments. Recognized for strategic leadership, technical excellence, and a customer-centric approach that delivers exceptional business results. Proven ability to build and lead high-performing teams, develop and execute impactful strategies, and foster a culture of continuous improvement and innovation.

  \begin{itemize}
    \setlength\itemsep{-0.5em}
    \item \textit{Strategic Leadership}: Expert in setting and executing strategic vision, leading cross-functional teams, and driving organizational growth.
    \item \textit{Innovation and Transformation}: Skilled in leveraging emerging technologies, including IoT and AI, to drive digital transformation and competitive advantage.
    \item \textit{Customer-Centric Solutions}: Adept at understanding customer needs, developing tailored solutions, and enhancing customer satisfaction and retention.
    \item \textit{Revenue Growth and Optimization}: Proven track record of driving significant revenue growth and optimizing operational efficiency through strategic initiatives.
    \item \textit{Thought Leadership}: Regular speaker at industry conferences and contributor to leading tech publications.
    \item % 9x Ignite/Build/Re:Invent speaker - includ keynote
  \end{itemize}
  
\end{rSection}

% Patterns and practices
% DEI
% Team Growth / Mentoring

%----------------------------------------------------------------------------------------
%	Experience
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Overview}
  
  \begin{rCompany}{Wind River Systems}{}{}

<<<<<<< HEAD
    \begin{rSubSubsection}{Head of Partner Enablement and Engineering}{Global Partnerships and Ecosystem}{January 2024 - Present}
      % dollar value gained - SAIC
      % Partner growth
      % Solutions created - lead aws/azure partnership
      % Model/Coach/Care?
      \item Drove transformation towards a scalable partner-driven business model by establishing a new Engineering and Enablement organization --- Doubling our active partner ecosystem and growing partner-influenced revenue by 173\%.
      \item Enabled partners to secure \$1.8B in revenue and an additional \$7.2B in renewable USG/DoD contracts by developing strategy and solutions enabling modernization of embedded development and testing, responsible for strategic differentiation.
      \item Model, Coach, Care
      \item Led efforts to integrate Wind River's products into partner ecosystems, including bringing critical tooling to DevSecOps platforms like GitHub, Azure DevOps, and GitLab, and enabling our operating systems on AWS and Azure. These enabled expansion through new and novel use cases while providing an enhanced developer experience.
      \item Developed and implemented partner training programs, improving partner capabilities and satisfaction.
      
      \item % Money Realized
      \item Led support of our partners in strategic USG/DoD bids. Provided strategy and solutions  responsible for strategic differentiation leading our partners to secure \$1.8B/yr in additional revenue from \$9B is renewable contracts.
      \item Oversaw engineering efforts to integrate partner solutions with Wind River's products, increasing market reach and customer satisfaction.
      \item Championed the adoption of emerging technologies, such as AI and edge computing, within partner solutions, resulting in innovative, high-impact offerings.
      \item Fostered a culture of continuous improvement and collaboration, leading to a 20\% increase in partner engagement and performance.
=======
    \begin{rSubSubsection}{Head of Partner Enablement and Engineering}{}{January 2024 - Present}
      \item Drove our evolution towards a scalable partner-centric business model by establishing a new Engineering and Enablement organization --- doubling our active partner ecosystem and growing partner-influenced revenue by 173\%.
      \item Enabled partners to strategically differentiate and secure \$1.8B in new revenue plus an additional \$7.2B in renewable USG/DoD contracts by leading a revolutionary approach to developing and testing mission-critical software.
      \item Expanded Wind River's Serviceable Obtainable Market (SOM) by over \$100M through key partner ecosystem integrations, including bringing critical tooling to DevSecOps platforms like GitHub, Azure DevOps, and GitLab, and enabling our operating systems to be delivered through hyperscaler marketplaces such as AWS and Azure.
>>>>>>> 5436854 (cloudspace and unikey updates)

    \end{rSubSubsection}
    
    \begin{rSubSubsection}{Global Director of Solutions Architecture}{}{January 2023 - January 2024}

      \item Established a global organization responsible for modernizing customers' edge platform, application, and AI/ML development lifecycle, including technical sales, support, and customer-focused product and engineering efforts.
      \item Directed development of a new suite of cloud-native DevSecOps tools, generating \$30M+/yr in new direct revenue opportunities and enabling strategic partners to pursue \$1B+ in commercial and DoD customer contracts.
      \item Spearheaded the implementation of agile methodologies, reducing project timelines by 20\% and increasing customer satisfaction.
      \item Led development of new processes to advocate for the voice of the customer across sales, product, and engineering, resulting in a 15\% increase in customer retention.
      \item Coached individuals and teams, fostering growth in interpersonal, technical, and leadership skills, contributing to a 25\% improvement in team performance.

    \end{rSubSubsection}
  \end{rCompany}

  \begin{rCompany}{Microsoft}{}{}

    \begin{rSubSubsection}{Senior Principal Architect and Head of Product Strategy}{Azure IoT}{January 2022 - January 2023}

        \item Drove product strategy for Azure IoT, leading cross-organizational program efforts spanning numerous CVPs.
        \item Developed new revenue measurement, COGS optimization, and customer acquisition strategies, resulting in 80\% YoY growth, 150M+ active devices, and \$500M+ in pull-through revenue.
        \item Presented Azure IoT keynotes at Microsoft Build, partner and industry conferences, EBCs, and more, establishing thought leadership in the IoT space.
        \item Spearheaded analyst reviews such as Gartner MQ and Forrester Wave, achieving leading positions for Edge and IIoT, enhancing Microsoft's market reputation.
        \item Championed a culture of innovation and collaboration, leading to the successful launch of several high-impact initiatives.
    
    \end{rSubSubsection}
    
    \begin{rSubSubsection}{Azure IoT Global Black Belt}{Global Customer Success}{December 2019 - January 2022}
       % Revenue metrics?
        \item Drove well-architected IoT solutions at strategic industrial customers responsible for >\$20M/yr in project revenue. 
        \item Developed a cost-effective, scalable, pattern for connected manufacturing. Led implementation initiatives across several dozen plants --- saving customers >\$10M/yr in production costs and improving line throughput by >17\%. 
        \item Provided technical expertise enabling customers to rapidly scale, growing monthly IoT service utilization by 760\%.
        \item Grew monthly customer project revenue by over 350\% by cultivating deep relationships and leveraging them to "land and expand" --- onboarding a multitude of new projects and leading to over \$100M in future revenue commitments.\
        \item Led strategic manufacturing partnerships with PTC and Rockwell to develop effective cross-company solutions.
    \end{rSubSubsection}
    
    \begin{rSubSubsection}{Enterprise Architect - Azure}{Microsoft Technology Centers}{April 2018 - December 2020}
        \item Guided architecture of customer solutions leveraging infrastructure, cloud-native application, and data platforms.
        \item Led opportunities with numerous Fortune 500 companies, securing over \$100M in Azure commitments, contributing to Microsoft's revenue growth.
        \item Established a cross-organizational team within Microsoft to learn and share customer engagement best practices, fostering a culture of continuous improvement.
        \item Delivered technical workshops and training sessions, enhancing customers' understanding and adoption of Azure solutions.
    \end{rSubSubsection}
  \end{rCompany}

  \begin{rCompany}{UniKey Technologies}{}{}

    \begin{rSubSubsection}{Engineering Manager}{Cloud Services}{May 2015 - December 2017}
      \item Led development of the first cloud-based IoT platform for physical access control, powering 1M+ connected devices and enabling keyless door entry (as seen on Shark Tank) for millions of residential and commercial customers.
      \item Grew a team of 10 developers and guided them in taking advantage of new cloud-native Azure services, enabling development and operation of a scalable, reliable, secure, and cost-effective platform with minimal headcount.
      \item Defined a robust architecture for handling large-scale persistent WebSocket connections from web, mobile, and IoT devices. Implemented actors and async messaging patterns to efficiently process thousands of messages per second.
      \item Collaborated with our security and embedded architects to design a robust zero-trust end-to-end public key infrastructure enabling secure communication between phones, locks, gateways, servers, and more.
      \item Led strategic technical partnerships and drove integrations with Amazon Alexa, Google Nest, Samsung SmartThings, and more, enabling novel customer smart-home capabilities and greatly expanding market reach.
      \item Guided cultural change during rapid company growth, resulting in improved team morale, collaboration, and quality.
    \end{rSubSubsection}
  \end{rCompany}

  \begin{rCompany}{Cloudspace}{}{}

    \begin{rSubSubsection}{Software Engineering Lead}{Web and Mobile}{September 2012 - May 2015}
      \item Led teams developing web and mobile applications, resulting in the launch of multiple high-impact customer projects including the \#1 ranked iOS food and drink app in the U.S. with more than 15 million monthly active users.
      \item Implemented company-wide quality standards and DevOps practices, leading to significant productivity gains.
      \item Mentored junior developers, fostering a culture of collaboration, continuous learning, and professional growth.
    \end{rSubSubsection}
  \end{rCompany}

  \begin{rNewRole}{Cloudspace}{Lead Software Engineer}{September 2012 - May 2015}
    \item Led development teams building web/mobile applications, resulting in the successful launch of multiple high-impact projects.
    \item Spearheaded the company transition to cloud-native services, improving scalability and performance.
    \item Implemented company-wide quality standards and DevOps practices, leading to significant productivity gains and reducing deployment times by 30\%.
    \item Mentored junior developers, fostering a culture of continuous learning and professional growth.
    \item Collaborated with clients to understand their needs and deliver tailored solutions, resulting in increased customer satisfaction.
  \end{rNewRole}
  
  %------------------------------------------------
  
  \begin{rCompany}{Software Engineer / Consultant}{July 2008 - September 2012}{}

  \end{rCompany}
  
  %------------------------------------------------
  
  
\end{rSection}

%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------
\vspace{0.5em} % Some space after the list of bullet points
\begin{rSection}{Education}
  
  {\bf University of Central Florida } Bachelor of Science --- Computer Science; Information Technology
  
\end{rSection}

\end{document}
